---
title: "Agroforestry Decision-Making"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# examples with shape and raster files using a partial protected areas shape file and raster for mean annual temperature in the US
library(dplyr)
library(sf)
library(maps)
library(ggplot2)
library(raster)

```

## Protected areas and mean annual temp
First we downloaded our proteced area data from the World Database on Protected Areas
We also have access to some sample climatic variables (temp, in this case):

```{r packages}
prot_areas <- st_read('usa_protected_areas/usa_protected_areas.shp')

mean_temp11 <- raster('mean_annual_temp/bio1_11.bil')
mean_temp12<- raster('mean_annual_temp/bio1_12.bil')
mean_temp13<- raster('mean_annual_temp/bio1_13.bil')

```

## Plotting and Reprojecting

We want to plot the protected areas and reproject the shapefile to add a l km buffer.

```{r merge_projection, echo=FALSE}
#merge into one file
mean_12_11<-merge(mean_temp11, mean_temp12)
mean_ann_temp<-merge(mean_12_11, mean_temp13)

# projection of shape file so that can do buffer in meeters
st_crs(prot_areas)

prj <- '+proj=aea +lat_1=29.5 +lat_2=45.5+lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0+units=m +no_defs'

prot_areas <- st_transform(prot_areas, crs = prj)
plot(prot_areas)
```

We add a buffer around the protected area and then retransform to extract the climate variables from the protected areas we're interested in.

```{r buffer_reproject}
# buffer by 1 km
buffer_prot_area<- st_buffer(prot_areas, 1000)

# raster projection
crs(mean_temp12)
# doesnsn't have anything included but i know that it is lat long projection

# tranform back to lat long project so can get extraction
buffer_prot_area <- st_transform(buffer_prot_area, crs = 4326)

# only did 2 protected areas here as an example
sample_temp <-extract(mean_temp12, buffer_prot_area[5:6,], fun=mean)
rownames(sample_temp) <- buffer_prot_area$NAME[5:6] # name rows by protected area

#mean temperatures for two protected areas
head(sample_temp)
```

Next we need to crop the buffered protected area to the extent of the climate variables...
or we can extract the temperature by state

```{r masking_selection, echo=FALSE}

st_crop(buffer_prot_area, extent(mean_ann_temp))

# group protected areas by state
state_prot_areas<-buffer_prot_area %>%
  group_by(SUB_LOC) %>%
  summarize(geometry=st_union(geometry))

# extracting temperature by state for and getting average
extract(mean_temp12, state_prot_areas, fun=mean, na.rm= T)

```

## Mapping the protected areas and mean temperature
```{r map, echo=T}

#  base R
plot(mean_temp12)
plot(buffer_prot_area[,"PARENT_ISO"], add=TRUE)

#  ggplot
ggplot(data=prot_areas) +
  geom_polygon(data=map_data("state"), 
               aes(x=long, y=lat, group=group), fill='white', col='black') +
  geom_sf(aes(fill = SUB_LOC)) +
  theme(legend.position = 'none')


```

